---
title: "Foundr Vignette"
author: "Brian Yandell"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(foundr)
```

## Sample Data
```{r}
sampleSignal <- partition(sampleData)
```

```{r}
sampleStats <- strainstats(sampleData)
sampleStats %>%
  filter(term == "signal")
```

- C on A: mostly signal
  + mean cor = 0.0107; signal cor = 0.90
  + -10*log(p.value) = 1.97, 2.81
- D on B: negligible signal
  + mean cor = 0.8110; signal cor = 0.28
  + -10*log(p.value) = 0.32, 2.73

## Scatterplots

#### Plots of Means

```{r}
out <- traitSolos(sampleData, sampleSignal,
                  response = "cellmean")
summary(out)
```

```{r}
plot(out)
```

```{r}
out2 <- traitPairs(
  out,
  traitnames = attr(out, "traitnames"),
  pair = c(
    paste(attr(out, "traitnames")[1:2], collapse = " ON "),
    paste(attr(out, "traitnames")[3:4], collapse = " ON ")))
plot(out2, parallel_lines = TRUE)
```

```{r}
out <- traitSolos(sampleData, sampleSignal,
                  response = "signal")
plot(out)
```

```{r}
out2 <- traitPairs(
  out,
  traitnames = attr(out, "traitnames"),
  pair = c(
    paste(attr(out, "traitnames")[1:2], collapse = " ON "),
    paste(attr(out, "traitnames")[3:4], collapse = " ON ")))
plot(out2)
```

# Correlations and Effects

```{r}
volcano(sampleStats, "signal")
```

```{r}
summary(sampleStats)
```

```{r}
summary(sampleStats, "deviation", "parts")
```

```{r}
summary(sampleStats, "log10.p", "terms")
```

```{r}
summary(sampleStats, "log10.p", "terms", threshold = NULL)
```

```{r}
effectplot(sampleStats, trait_names(sampleStats, "C"))
```

# Shiny App

This package is equiped with a default app in [inst/shinyApp/app.R](https://github.com/byandell/foundr/blob/main/inst/shinyApp/app.R).
Other applied apps can be found in <https://github.com/byandell/FounderCalciumStudy> and
<https://github.com/byandell/FounderDietStudy>. Users can deploy their own version of apps.

More is needed here to explain the steps to set up:

- harmonize data with [harmonize()](https://github.com/byandell/foundr/blob/main/R/harmonize.R); see example in <https://github.com/byandell/FounderCalciumStudy/blob/main/DataHarmony.Rmd>.
- customize app.r; see example in <https://github.com/byandell/FounderCalciumStudy/blob/main/app.R> with components
  + install packages for the deployment platform that are not already present
  + read in trait data created in harmonize step
  + set `customSettings`
  + provide custom title to `foundr::foundrUI()`
