---
title: "Calcium"
author: "Brian Yandell"
date: "2023-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(foundr)
```

```{r}
datadir <- "../../../attie_alan/FounderCalciumStudy"
```

```{r}
traitData <- readRDS(file.path(datadir, "traitData.rds")) %>%
  rename(dataset = "datatype")
traitStats<- readRDS(file.path(datadir, "traitStats.rds")) %>%
  rename(dataset = "datatype")
traitSignal <- readRDS(file.path(datadir, "traitSignal.rds")) %>%
  rename(dataset = "datatype")
```

```{r}
td <- traitData %>% filter(grepl("freq_8_2|Fbp1_PP_5480", trait))
tst <- traitStats %>% filter(grepl("freq_8_2|Fbp1_PP_5480", trait))
tsi <- traitSignal %>% filter(grepl("freq_8_2|Fbp1_PP_5480", trait))
```

```{r}
(traitnames <- unique(foundr:::unite_datatraits(tsi)))
```

```{r}
tsolo <- traitSolos(td, tsi)
```

```{r}
summary(tsolo)
```

```{r}
plot(tsolo)
```

```{r}
tsolo8 <- traitSolos(td, tsi, traitnames[1:3])
```

```{r}
summary(tsolo8)
```

```{r}
plot(tsolo8)
```

```{r}
summary(traitSolos(td, tsi, traitnames[c(2,1,3)]))
```

```{r}
plot(traitSolos(td, tsi, traitnames[1:3]))
```

```{r}
tra <- traitSolos(td, tsi, traitnames[3:1])
```

```{r}
summary(tra)
```

```{r}
plot(tra)
```

# Pairs

Want traitPairs etc. to have features of selectTrait. It does not appear to be working well when conditions don't align.

- add line for mean and signal approaches
- traitPairs computes mean right now--want to use selectTrait

```{r}
tds <- traitSolos(td, tsi, traitnames[c(1,4)], response = "mean")
```

```{r}
out <- traitPairs(tds)
```

Seems to mostly work. Hardwired response = value and mean. Need to fix that.

```{r}
out <- traitPairs(tra, traitnames = attr(tra, "traitnames"))
```

```{r}
ggplot_traitPairs(out)
```

```{r}
tmp <- traitSolos(td, tsi, traitnames[c(4,5)], response = "mean")
tmp2 <- traitPairs(tmp)
plot(tmp2)
```

```{r}
plot(traitPairs(traitSolos(td, tsi, traitnames[c(5,4)], response = "signal")))
```

# Effects Plots

```{r}
effectplot(tst)
```

# Correlation

bestcor only considers other data that agrees with condition arrangement
How to refactor to get correlations across conditions?

One challenge is that the nqrank gives different values, but here we even see different signs to correlation! **TRY ON RAW DATA**

Error: 'x' must be numeric (when both protein and calcium8G used for 5,4)

Error: Faceting variables must have at least one value

```{r}
bestcor(tsi, traitnames[4]) %>%
  select(-absmax)
```

```{r}
bestcor(tsi %>% filter(trait %in% traitnames[c(2,4)]), traitnames[4]) %>%
  select(-absmax)
```

```{r}
bestcor(tsi %>% filter(trait %in% traitnames[c(3,4)]), traitnames[4]) %>%
  select(-absmax)
```

```{r}
bestcor(tsi %>% filter(trait %in% traitnames[1:4]), traitnames[4]) %>%
  select(-absmax)
```

The following seems to get it wrong--why?

```{r}
bestcor(tsi %>% filter(trait %in% traitnames[4:5]), traitnames[4]) %>%
  select(-absmax)
```

```{r}
bestcor(tsi, traitnames[4]) %>%
  select(-absmax)
```

## multiple traits with different condition situations

```{r}
bc <- bestcor(tsi, traitnames[c(5,4)])
```

```{r}

```{r}
bc <- bestcor(tsi, traitnames[c(1,4)])
```

```


